Reanalysis Step 2: Multiple Imputation

### 2025-08-30 reanalysis-2-multiple_imputation.qmd
consistent person dr

  # Copy person_dr_max back to person_dr for each eye
  # This ensures DR severity is consistent within patients
  # Handle the factor conversion correctly
  imp_data <- imp_data |>
    mutate(
      # person_dr_max is an ordered factor with levels "No_DR", "NPDR", "PDR"
      # Convert to numeric 0, 1, 2
      person_dr = case_when(
        person_dr_max == "No_DR" ~ 0,
        person_dr_max == "NPDR" ~ 1,
        person_dr_max == "PDR" ~ 2,
        TRUE ~ NA_real_
      )
    ) |>
    select(-person_dr_max)  # Remove person_dr_max after using it

@@

>>>>

@@

# FINAL STEP: Enforce person_dr consistency across all datasets
# Take the maximum person_dr value per patient to ensure consistency
imputed_datasets <- lapply(imputed_datasets, function(imp_data) {
  # Calculate max person_dr per patient
  person_dr_max_lookup <- imp_data |>
    group_by(e_mrn_deidentified) |>
    summarise(
      person_dr_max_value = max(person_dr, na.rm = TRUE),
      .groups = 'drop'
    )

  # Replace person_dr with the consistent max value
  imp_data <- imp_data |>
    left_join(person_dr_max_lookup, by = "e_mrn_deidentified") |>
    mutate(person_dr = person_dr_max_value) |>
    select(-person_dr_max_value)

log_message("Enforced person_dr consistency by taking max value per patient")
